Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-14 cosmic_voids.tex
empezando con las conclusiones
New figure of abundance of over and subcompensated voids vs effective radius.

%.........................................................................
%FIGURE 3: volume functions
\begin{figure}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_regions_volume_all.pdf}

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogues. FA-T-web (red curves), FA-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

@@

\end{figure}
%.........................................................................

@@

>>>>

%.........................................................................
%FIGURE 3: volume functions
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_regions_volume_all.pdf}
  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_regions_volume_compensated.pdf}

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogues. FA-T-web (continuous red curves), FA-Vweb (dashed blue 
  curves). Left panel, total distributions. Right panel, distributions of 
  subcompensanted and overcompensanted voids. }

@@

@@

We propose in this paper a new method to find and describe void in
cosmological dark matter simulations.
The basis of our metho is the anisotropy of the eigenvalues from tensors
constructed to describe the cosmic web.
